%*****************************************
\chapter*{Preface}\label{preface}
%*****************************************

I have taught CIS 221, \textit{Digital Logic}, for Cochise College since about 2003 and enjoy working with students on this topic. From the start, I wanted students to work with labs as part of our studies and actually design circuits to complement our theoretical instruction. As I evaluated circuit design software I had three criteria:

\begin{itemize}
  \item \textbf{\ac{OER}}. It is important to me that students use software that is available free of charge and is supported by the entire web community. 
  \item \textbf{Platform}. While most of my students use a Windows-based system, some use Macintosh and it was important to me to use software that is available for both of those platforms. As a bonus, most OER software is also available for the Linux system, though I'm not aware of any of my students who are using Linux.
  \item \textbf{Simplicity}. I wanted to use software that was easy to master so students could spend their time understanding digital logic rather than learning the arcane structures of a simulation language.
\end{itemize}

I originally wrote a number of lab exercises using \textit{Logisim}, but the creator of that software, Carl Burch, announced that he would quit developing it in 2014. Because it was published as an open source project, a group of Swiss institutes started with the \textit{Logisim} software and developed a new version that integrated several new tools, like a chronogram, and released it under the name \LE.

It is my hope that students will find these labs instructive and the labs enhance their learning of digital logic. This lab manual is written with \LaTeX\ and published under a \href{https://creativecommons.org/publicdomain/zero/1.0/}{Creative Commons Zero} license with a goal that other instructors can modify it to meet their own needs. The source code can be found at \href{https://github.com/grself/CIS221_Lab_Manual}{my personal GITHUB page} and I always welcome comments that will help me improve this manual.

\bigskip
\begin{flushright}
  \textemdash  George Self
\end{flushright}


