%*******************************************************
% Declaration
%*******************************************************
\refstepcounter{dummy}
\pdfbookmark[0]{Style Guide}{styleguide}
\chapter*{Style Guide}
\thispagestyle{empty}

\begin{itemize}

  \item \textsc{Boolean Expressions}. Use math equations for in-line Boolean expressions and equations.

	\item \textsc{Circuit/Subcircuit Name}. Use  \lstinline[columns=fixed]|Circuit_4|.

  \item \textsc{Figures and Tables}.
  
  \begin{itemize}
    \item Figures and Tables use an [H] specification
    \item Captions go at the end of the table block so it is printed under the table to match figures and listings. (Figures and Listings place the caption under by default)
  \end{itemize}

  \item \textsc{File Names}. File names should be in Typewriter and Emphasis styles: \emph{\texttt{Lab01\_Mux21}}.

	\item \textsc{Library Devices}. Devices (like counters) in regular font but with the italicized library name following, like: Counter (\textit{Memory} library).

	\item \textsc{Gates}. Should be in all caps and typewriter font: \texttt{AND}
  
  \item \textsc{Menu Items}. Use small caps: \textsc{Simulate -> Reset Simulation}.  

  \item \textsc{Numbers}. 

	\begin{itemize}
		\item Numbers use normal font, not math or some other special font.
		\item Spell out numbers up to ten; thus, not ``1s,'' but ones.
		\item Larger numbers with a suffix, like ``s,'' do not use an apostrophe: not ten's, but tens.
	\end{itemize}

  \item \textsc{Pin Names}. Pin names (like \textit{Q1}) are italicized. This is also true for variable names and types of flip-flops.

  \item \textsc{Properties}. Properties (like \textit{Facing}) are italicized.

	\item \textsc{Signals}. Should be italicized in typewriter font: \textit{\texttt{Activate}}

  \item \textsc{Tools}. Tools (like \textit{Poke}) are capitalized and italicized.

  \item \textsc{True/False}. The words \emph{True} and \emph{False} are capitalized and in an \lstinline[columns=fixed]|\emph{}| block.

	\item \textsc{Vocabulary}
	
  \begin{itemize}
	\item ``Flip-flop'' is hyphenated
	\item ``Logisim-evoluation'' is placed in italics with only ``Logisim'' capitalized: \textit{Logisim-evolution}
	\item ``Subcircuit'' is not hyphenated
\end{itemize}	

\end{itemize}

